---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# perutranspaeconomica

<!-- badges: start -->
<!-- badges: end -->

El objetivo de perutranspaeconomica es contar con una manera de obtener datos del Portal de Transparencia Económica Perú desde R, con una interfaz de programación consistente y clara.

## Code of Conduct

Please note that the perutranspaeconomica project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.


## Installation

You can install the development version of perutranspaeconomica from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("calderonsamuel/perutranspaeconomica")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example, eval=FALSE}
library(perutranspaeconomica)
## basic example code
```


